Evaluating FAIR Digital Object and Linked Data as distributed object systems

### 2023-06-15 latex/table1.tex
more bib tweaks.

\begin{minipage}[b]{\linewidth}\raggedright
\emph{Quality}
\end{minipage}
  & \begin{minipage}[b]{\linewidth}\centering
FDO w/ DOIP
\end{minipage}
  & \begin{minipage}[b]{\linewidth}\centering
Web w/ Linked Data
\end{minipage} \\

@@

  & DOIP \autocite{foundationDigitalObjectInterface} is transport-independent, commonly TLS TCP/IP port 9000), \href{https://www.cordra.org/documentation/api/doip-api-for-http-clients.html}{DOIP over HTTP}

>>>>

\emph{Quality} & 
FDO w/ DOIP & 
Web w/ Linked Data \\

@@

  & \textcite{foundationDigitalObjectInterface} is transport-independent, commonly TLS TCP/IP port 9000), \href{https://www.cordra.org/documentation/api/doip-api-for-http-clients.html}{DOIP over HTTP}
